Assessing Power of the California Microhap Baseline for PBT and relationship inference

### 2024-07-08 003-ckmr-sim-evaluation.Rmd
Rename some notebooks

```{r}
if(exists("snakemake")) {
  input_list <- snakemake@input
  output_list <- snakemake@output
} else {
  input_list <- list(
    final_baseline = "data/subRoSA_baseline_rubias_loci_renamed_July_2024.csv.gz",
    lfar_genos = "data/metagenos_hap2col_lfar_all_samps.csv",
    pop_labels = "inputs/reference-collection-names.csv",
    locus_info = "inputs/Calif-Chinook-Amplicon-Panel-Information.csv"
  )
  output_list <- list(
    ckmr_figure = "results/ckmr-sim-eval/fpr-fnr-figure.pdf",
    ckmr_figure_crop = "results/ckmr-sim-eval/fpr-fnr-figure-crop.pdf",
    ckmr_figure_tex = "tex/images/fpr-fnr-figure-crop.pdf",
    ckmr_comp = "results/ckmr-sim-eval/cmkr-comp-figure.pdf",
    ckmr_comp_crop = "results/ckmr-sim-eval/cmkr-comp-figure-crop.pdf",
    ckmr_comp_tex = "tex/images/cmkr-comp-figure-crop.pdf"

>>>>

```{r}
if(exists("snakemake")) {
  input_list <- snakemake@input
  output_list <- snakemake@output
} else {
  input_list <- list(
    final_baseline = "data/subRoSA_baseline_rubias_loci_renamed_July_2024.csv.gz",
    pop_labels = "inputs/reference-collection-names.csv",
    locus_info = "inputs/Calif-Chinook-Amplicon-Panel-Information.csv"
  )
  output_list <- list(
    ckmr_figure = "results/ckmr-sim-eval/fpr-fnr-figure.pdf",
    ckmr_figure_crop = "results/ckmr-sim-eval/fpr-fnr-figure-crop.pdf",
    ckmr_figure_tex = "tex/images/fpr-fnr-figure-crop.pdf",
    ckmr_comp = "results/ckmr-sim-eval/cmkr-comp-figure.pdf",
    ckmr_comp_crop = "results/ckmr-sim-eval/cmkr-comp-figure-crop.pdf",
    ckmr_comp_tex = "tex/images/cmkr-comp-figure-crop.pdf"
